---
title: "Getting started with fdb"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with fdb}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Overview

The `fdb` package implements likelihood-informed frequentist dynamic borrowing
methods for hybrid-control survival trials. The borrowing strength is governed
by a single tuning parameter, $\lambda$, acting on a drift parameter $\delta$
that captures population shift between concurrent and external controls under
a Cox proportional hazards model.

This vignette walks through:

1. Simulating a hybrid-control dataset;
2. Fitting all borrowing methods on a single dataset;
3. Running a small Monte Carlo study;
4. Performing design-stage $\lambda$ calibration with the one-stop wrapper.

All chunks below are set to `eval = FALSE` so that the vignette builds quickly
on CRAN. Run them interactively or with `eval = TRUE` to reproduce.

# 1. Simulate a hybrid-control trial

```{r}
library(fdb)

set.seed(1)
sim <- simulate_hybrid_cox(
  nI1 = 150, nI0 = 150, nE = 300,
  theta0 = log(0.8), delta0 = log(1.1),
  p = 5, beta = rep(0.2, 5)
)
head(sim$data)
```

The simulated data frame has columns `time`, `status`, `T` (treatment
indicator), `Z` (external-control indicator), and `X1, ..., Xp` (covariates).

# 2. Fit all borrowing methods on one dataset

```{r}
res <- fit_all_methods(
  sim$data,
  lambda_li = 0.2, lambda_p1 = 0.2,
  lambda_p2 = 0.2, lambda_p3 = 0.2, lambda_p4 = 0.2
)
res
```

The returned data frame reports both model-based standard errors (`se_theta`)
and penalized estimating-equation sandwich standard errors (`se_sand`).

# 3. Monte Carlo study under a fixed scenario

```{r}
sim_out <- run_simulation(
  nsim = 100, scenario = scenario_S1,
  lambdas = lambdas_default,
  alpha = 0.025, seed = 1
)
subset(sim_out$summary, inference == "sandwich")
```

# 4. Design-stage $\lambda$ calibration

```{r}
study <- run_fdb_study(
  scenario_base   = scenario_S1,
  drift_hr_range  = c(0.8, 1.2),
  drift_by_hr     = 0.1,
  alpha           = 0.025,
  alt_hr          = 0.8,
  do_calibration  = TRUE,
  nsim_cal        = 300,
  nsim_curve      = 500,
  parallel        = FALSE,
  seed            = 1
)
study$calibration$lambda_star
study$type1_curve
study$power_curve
```

For production runs, use larger `nsim_cal` and `nsim_curve`, and enable
`parallel = TRUE` together with `ncores`.
